---
title: "Simulating active cross-situational learning"
author: "George Kachergis"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

RUN_MODELS = FALSE # re-run the models? (warning: slow)

Cs = c(10, 50, 100, 200, 500)
Ms = c(1000)
```

We will start start by simulating learning of a vocabulary of size M = 1000 words with varying context sizes (i.e., number of referents in each scene: C = {10, 50, 100, 200, 500}). 
We will consider two different models: an eliminative model, and a ranked frequency model.

## Eliminative model

On each appearance of a word, this model eliminates any referents that are not present in the scene.

```{r run-eliminative, eval=RUN_MODELS}
source("corpusXSL_eliminative_active_parallel.R")
REPS = 10
act_sim = run_sim_grid(Cs, Ms, uniform=T, active=T, fam_context=F, reps=REPS)
act_famcon_sim = run_sim_grid(Cs, Ms, uniform=T, active=T, fam_context=T, reps=REPS) 
act_nonunif_sim = run_sim_grid(Cs, Ms, uniform=F, active=T, fam_context=F, reps=REPS) 
act_nonunif_famcon_sim = run_sim_grid(Cs, Ms, uniform=F, active=T, fam_context=T, reps=REPS) 

pass_sim = run_sim_grid(Cs, Ms, uniform=T, active=F, fam_context=F, reps=REPS) 
pass_famcon_sim = run_sim_grid(Cs, Ms, uniform=T, active=F, fam_context=T, reps=REPS) 
pass_nonunif_sim = run_sim_grid(Cs, Ms, uniform=F, active=F, fam_context=F, reps=REPS) 
pass_nonunif_famcon_sim = run_sim_grid(Cs, Ms, uniform=F, active=F, fam_context=T, reps=REPS) 

agg <- rbind(act_sim, act_famcon_sim, act_nonunif_sim, act_nonunif_famcon_sim,
             pass_sim, pass_famcon_sim, pass_nonunif_sim, pass_nonunif_famcon_sim)
aggl <- agg %>% gather("decile", "episodes", 7:16)

pd <- aggl %>% group_by(C, M, active, uniform, fam_context, decile) %>%
  tidyboot::tidyboot_mean(episodes)

save(aggl, pd, file="passive_active_eliminative_1000.RData")
```

```{r plot-eliminative, echo=F}
load("passive_active_eliminative_1000.RData")

dodge = position_dodge(width = 2)
pd$dec = rep(seq(10, 100, 10), nrow(pd) / 10) # 
ggplot(pd, aes(x=dec, y=mean, group=C, color=C)) + geom_point(position = dodge) + 
  geom_line(position = dodge) + # add active ...
  facet_grid(fam_context ~ uniform ) + theme_bw() + xlab("Percent of Vocabulary Learned") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper, color=C), position = dodge) + 
  ylab("Mean Number of Episodes") 
#ggsave("passive_active_eliminative_1000.pdf", width=6, height=6)
```


## Ranked frequency model

This model tracks co-occurrences, and learns a word-referent mapping as soon as the co-occurrence of that word and referent is greater than any other referent with that word.

```{r run-rankedFreq, eval=RUN_MODELS}
source("corpusXSL_rankedFreq_active_parallel.R")

#act_sim =  run_sim_grid(Cs, Ms, uniform=T, active=T, fam_context=F, reps=10) # always =M
#act_nonunif_sim = run_sim_grid(Cs, Ms, uniform=F, active=T, fam_context=F, reps=10) 

pass_sim = run_sim_grid(Cs, Ms, uniform=T, active=F, fam_context=F, reps=REPS) 
pass_famcon_sim = run_sim_grid(Cs, Ms, uniform=T, active=F, fam_context=T, reps=REPS) 
pass_nonunif_sim = run_sim_grid(Cs, Ms, uniform=F, active=F, fam_context=F, reps=REPS) 
pass_nonunif_famcon_sim = run_sim_grid(Cs, Ms, uniform=F, active=F, fam_context=T, reps=REPS) 

agg <- rbind(pass_sim, pass_famcon_sim, pass_nonunif_sim, pass_nonunif_famcon_sim)
aggl <- agg %>% gather("decile", "episodes", 7:16)

pd <- aggl %>% group_by(C, M, active, uniform, fam_context, decile) %>%
  tidyboot::tidyboot_mean(episodes)

save(aggl, pd, file="passive_rankedFreq_1000.RData")
```



```{r, plot-rankedFreq, echo=F}
load("passive_rankedFreq_1000.RData")

dodge = position_dodge(width = 2)
pd$dec = rep(seq(10, 100, 10), nrow(pd) / 10) # 100 should be 99
ggplot(pd, aes(x=dec, y=mean, group=C, color=C)) + geom_point(position = dodge) + 
  geom_line(position = dodge) + 
  facet_grid(fam_context ~ uniform ) + theme_bw() + xlab("Percent of Vocabulary Learned") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper, color=C), position = dodge) + 
  ylab("Mean Number of Episodes") 
#ggsave("passive_rankedFreq_1000.pdf", width=6, height=6)
```

This model shows no effect of selecting a familiar context.
